Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs with the Uniform Kernel

### 2016-03-01 main_paper.tex
Make some minor formatting and text tweaks
Fix minor spelling errors

The paper is organized as follows. Section~\ref{background} describes the basic
RD approach, its usual implementation, and the explicit analytical bias
correction approach in the literature. Section~\ref{boot} presents our proposed
bootstrap bias corrected RD algorithm and discusses its asymptotic
properties. Simulation evidence that the bootstrap procedure provides valid CIs
and its relative performance to the analytical bias correction are presented in
Section~\ref{sim} and Section~\ref{application} demonstrates the estimator's
usage by applying it to the Head Start dataset used
by~\cite{ludwig2007}.\footnote{%
  The simulations and empirical analysis were carried out in the R programming
  language \citep{R} and rely on the \textit{rdrobust} \citep{rdrobust},
  \textit{doParallel} \citep{doparallel}, \textit{foreach} \citep{foreach}, and
  \textit{doRNG} \citep{dorng} packages.} %
Finally, Section~\ref{conclusion} concludes.

@@

The Monte Carlo experiments have a similar structure. For all of them, we
generate 500 i.i.d.\ observations from the DGP
\begin{align*}
Y_{i}           &= \mu_{j}(X_{i}) + \varepsilon_{i} \\
X_{i}           &\sim  2 \times \betarv(2,4) - 1 \\
\varepsilon_{i} &\sim \normal(0, 0.1295^2),
\end{align*}
where $j$ will index the specific DGP. This is the experimental design used by
\citet{IK} and CCT, which we adopt here to make our simulation results directly
comparable with theirs and the rest of the literature. We
will use the same three functional forms for $\mu_{j}$ as CCT as well.

@@

For completeness, we also report the
original results in \cite{ludwig2007}.\footnote{%
  One minor issue arose in reproducing Ludwig and Miller's results: their paper
  presents results for the \emph{triangular} kernel, but we were only able to
  recover their ATE estimate using the \emph{uniform} kernel. Results for the
  triangular and uniform kernel were essentially the same, and this discrepency
  does not affect Ludwig and Miller's conclusions.} %
Since our research focuses on confidence intervals, we calculate and report
the conventional unadjusted RD confidence interval for each of the bandwidths
used by \cite{ludwig2007}. (Ludwig and Miller use a range of bandwidths
for their analysis.) They also use a paired bootstrap algorithm to generate
p-values, and we report those p-values for completeness.

@@

Bootstrap procedures are appealing in this setting because they are relatively
easy for applied researchers to modify to account for new and unusual dependence
structures or functional forms. The variance adjustment was proven to be correct
under the assumption of i.i.d.\ data, but could easily be extended to handle
cross-sectional or time series dependence by using the appropriate resampling
strategy on the second order polynomial's residuals. For the analytical methods,
however, new formulas need to be derived to accomodate new features of the
DGP. To fully take advantage of the bootstrap's flexibility, though, these
results need to be extended to other kernels, design strategies (e.g. fuzzy and
kink RD designs) and other more realistic dependence structures. All of these
are the subject of ongoing research.

\newpage
\appendix
\section{Mathematical appendix}
Let $e_p$ be the selection vector with 1 in element $p+1$ and 0
everywhere else. Define the following additional notation (largely
introduced by CCT): $r_p(x) = (1,\ x,\dots,\ x^p)'$,
\begin{align*}
  (\hat{\mu}_{+}(h),\ \hat{\mu}_{+}^{(1)}(h),\ \hat\mu_{+}^{(2)}(h))'
  &= \argmin_{\mu_0, \mu_1, \mu_2} \ssum[+]{i}{h}
    (Y_i - \mu_0 - \mu_1 X_i/h - \mu_2 (X_i/h)^2) \\
  (\hat{\mu}_{-}(h),\ \hat{\mu}_{-}^{(1)}(h),\ \hat\mu_{-}^{(2)}(h))'
  &= \argmin_{\mu_0, \mu_1, \mu_2} \ssum[-]{i}{h}
    (Y_i - \mu_0 - \mu_1 X_i/h - \mu_2 (X_i/h)^2)
\end{align*}
\begin{align*}
  \Gamma_{+,p}(h) &= \tfrac{1}{nh} \ssum[+]{i}{h} r_p(X_i/h) r_p(X_i/h)' \\
  \Gamma_{-,p}(h) &= \tfrac{1}{nh} \ssum[-]{i}{h} r_p(X_i/h) r_p(X_i/h)' \\
  \Psi_{+,p,q}(h,b)
  &= \tfrac{1}{nhb} \ssum[+]{i}{\min(h,b)} r_p(X_i/h) r_q(X_i/b)'
    \V(Y_i \mid X_i) \\
  \Psi_{-,p,q}(h,b)
  &= \tfrac{1}{nhb} \ssum[-]{i}{\min(h,b)} r_p(X_i/h) r_q(X_i/b)'
    \V(Y_i \mid X_i) \\
  \Bf_+(h)
  & = e_0' \Gamma_{+,1}^{-1}
    \ssum[+]{i}{h} r_1(X_i/h) \; X_i^2 / h^2, \\
  \Bf_-(h)
  & = e_0' \Gamma_{-,1}^{-1}
    \ssum[-]{i}{h} r_1(X_i/h) \; X_i^2 / h^2.
\end{align*}

>>>>

The paper is organized as follows. Section~\ref{background} describes the basic
RD approach, its usual implementation, and the explicit analytical bias
correction approach in the literature. Section~\ref{boot} presents our proposed
bootstrap bias corrected RD algorithm and discusses its asymptotic
properties. Simulation evidence that the bootstrap procedure provides valid CIs
and its relative performance to the analytical bias correction are presented in
Section~\ref{sim} and Section~\ref{application} demonstrates the estimator's
usage by applying it to the Head Start dataset used
by~\cite{ludwig2007}.\footnote{%
  The simulations and empirical analysis were carried out in the R programming
  language \citep{R} and rely on the \textit{rdrobust} \citep{rdrobust},
  \textit{doParallel}, \textit{foreach} \citep{doparallel,foreach}, and
  \textit{doRNG} \citep{dorng} packages.} %
Finally, Section~\ref{conclusion} concludes.

@@

The Monte Carlo experiments have a similar structure. For all of them, we
generate 500 i.i.d.\ observations from the DGP
\begin{align*}
Y_{i}           &= \mu_{j}(X_{i}) + \varepsilon_{i} \\
X_{i}           &\sim  2 \times \betarv(2,4) - 1 \\
\varepsilon_{i} &\sim N(0, 0.1295^2),
\end{align*}
where $j$ will index the specific DGP. This is the experimental design used by
\citet{IK} and CCT, which we adopt here to make our simulation results directly
comparable with theirs and with the rest of the literature. We
will use the same three functional forms for $\mu_{j}$ as CCT as well.

@@

For completeness, we also report the
original results in \cite{ludwig2007}.\footnote{%
  One minor issue arose in reproducing Ludwig and Miller's results: their paper
  presents results for the \emph{triangular} kernel, but we were only able to
  recover their ATE estimate using the \emph{uniform} kernel. Results for the
  triangular and uniform kernel were essentially the same, and this discrepancy
  does not affect Ludwig and Miller's conclusions.} %
Since our research focuses on confidence intervals, we calculate and report
the conventional unadjusted RD confidence interval for each of the bandwidths
used by \cite{ludwig2007}. (Ludwig and Miller use a range of bandwidths
for their analysis.) They also use a paired bootstrap algorithm to generate
p-values, and we report those p-values for completeness.

@@

Bootstrap procedures are appealing in this setting because they are relatively
easy for applied researchers to modify to account for new and unusual dependence
structures or functional forms. The variance adjustment was proven to be correct
under the assumption of i.i.d.\ data, but could easily be extended to handle
cross-sectional or time series dependence by using the appropriate resampling
strategy on the second order polynomial's residuals. For the analytical methods,
however, new formulas need to be derived to accommodate new features of the
DGP. To fully take advantage of the bootstrap's flexibility, though, these
results need to be extended to other kernels, design strategies (e.g. fuzzy and
kink RD designs) and other more realistic dependence structures. All of these
are the subject of ongoing research.

\appendix
\section{Mathematical appendix}
Let $e_p$ be the selection vector with 1 in element $p+1$ and 0
everywhere else. Define the following additional notation (largely
introduced by CCT): $r_p(x) = (1,\ x,\dots,\ x^p)'$,
\begin{align*}
  (\hat{\mu}_{+}(h),\ \hat{\mu}_{+}^{(1)}(h),\ \hat\mu_{+}^{(2)}(h))'
  &= \argmin_{\mu_0, \mu_1, \mu_2} \ssum[+]{i}{h}
    (Y_i - \mu_0 - \mu_1 X_i/h - \mu_2 (X_i/h)^2) \\
  (\hat{\mu}_{-}(h),\ \hat{\mu}_{-}^{(1)}(h),\ \hat\mu_{-}^{(2)}(h))'
  &= \argmin_{\mu_0, \mu_1, \mu_2} \ssum[-]{i}{h}
    (Y_i - \mu_0 - \mu_1 X_i/h - \mu_2 (X_i/h)^2)
\end{align*}
\begin{align*}
  \Gamma_{+,p}(h) &= \tfrac{1}{nh} \ssum[+]{i}{h} r_p(X_i/h) r_p(X_i/h)' \\
  \Gamma_{-,p}(h) &= \tfrac{1}{nh} \ssum[-]{i}{h} r_p(X_i/h) r_p(X_i/h)' \\
  \Psi_{+,p,q}(h,b)
  &= \tfrac{1}{nhb} \ssum[+]{i}{\min(h,b)} r_p(X_i/h) r_q(X_i/b)'
    \V(Y_i \mid X_i) \\
  \Psi_{-,p,q}(h,b)
  &= \tfrac{1}{nhb} \ssum[-]{i}{\min(h,b)} r_p(X_i/h) r_q(X_i/b)'
    \V(Y_i \mid X_i) \\
  \Bf_+(h)
  & = e_0' \Gamma_{+,1}^{-1}
    \ssum[+]{i}{h} r_1(X_i/h) \; X_i^2 / h^2, \\
  \Bf_-(h)
  & = e_0' \Gamma_{-,1}^{-1}
    \ssum[-]{i}{h} r_1(X_i/h) \; X_i^2 / h^2.
\end{align*}
